\documentclass{simplecv}
\usepackage[margin=1.3in]{geometry}


\begin{document}
\pagestyle{empty} 

\leftheader{LIMSI-CNRS\\BP 133\\91403 Orsay Cedex\\France
}

\rightheader{TEL: +33 (0) 1 69 85 81 84\\
\texttt{\small bredin@limsi.fr}\\
\texttt{\small http://herve.niderb.fr/}
}

\title{Herv\'{e} Bredin -- CNRS permanent researcher}

\maketitle

\vspace{-1cm}
\begin{center}
(last updated on July 22, 2012)
\end{center}

\section{Work Experience}

\begin{topic}
\item[2008--today] Researcher at National Center for Scientific Research (CNRS)

\emph{Multimodal fusion \& applications.} 

\begin{topic}
	\item[2010--today] Laboratoire d'Informatique pour la M\'{e}canique et les Sciences de l'Ing\'{e}nieur (Orsay, France)
	\item[2008--2010] Institut de Recherche en Informatique de Toulouse (Toulouse, France)
\end{topic}

Applications include video semantic indexing~\cite{Bredin2012a}, video structuring and summarization~\cite{Bredin2012}, and multimodal person recognition.

\textbf{Projects:} Quaero, QCompere/REPERE, IRIM/TRECVid

\item[2008 (jan.--sept.)] Post-doctoral researcher at Dublin City University,\\ Center for Digital Video Processing (Dublin, Ireland)

\emph{Automatic summarization of user-generated video content.}

\item[2006--2007] Assistant lecturer at Telecom ParisTech (Paris, France)

\emph{Pattern recognition and biometrics.}

\item[2004--2007] Ph.D. candidate at Telecom ParisTech (Paris, France).

\emph{Talking-face biometrics.}

\textbf{Projects:} BioSecure, SecurePhone 

\item[2004 (jun.--dec.)] Research intern at IBM Speech Group (La D\'{e}fense, France)

\emph{Canadian french text-to-speech phonetic front-end adaptation.}
\end{topic}

\section{Education}

\begin{topic}
\item[2007] Ph.D. thesis from Telecom ParisTech (Paris, France)

\emph{Making talking-face authentication robust to deliberate imposture.}

\item[2004] M.Eng. from Telecom ParisTech \emph{``Grande Ecole''} (Paris, France)

\emph{Pattern recognition, signal and image processing.}
\end{topic}

\section{Open-source Software}
\begin{topic}
\item[PyAnnote] Python module for collaborative annotation of multimedia content\\
\texttt{\small http://packages.python.org/PyAnnote}
\item[pinocchIO] File format, C library and set of tools for storing audiovisual document descriptors\\
\texttt{\small http://pinocchio.niderb.fr}
\item[PyAFE] Python toolkit for audio fingerprinting evaluation~\cite{Ramona2011}\\
\texttt{\small http://pyafe.niderb.fr}
\item[BioSecure] Talking-face reference system~\cite{Bredin2006a}\\
\texttt{\small http://biosecure.it-sudparis.eu}
\end{topic}

\section{Publications and Awards}

5 journal articles, 3 book chapters, 22 conference papers.\\
EBF European Biometrics Research Industry Award 2007~\cite{Bredin2008}

\section{Selected Publications}
\nocite{Bredin2012,Bredin2012a,Ramona2011,Bredin2009,Bredin2008,Bredin2007,Argones-Rua2007a,Bredin2006a}
\bibliographystyle{abbrv}
\bibliography{publi/bredin}

\end{document}
